Applying Discontinuous Petrov-Galerkin Methods to Fluid Problems

### 2012-03-23 docs/presentations/nate/Proposal/SIAMreport.tex
Updated Stokes write-up.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@387 36274a68-8941-4c93-80ef-affaed5139da

% DEFINITIONS ------------------------------------------------------------
% ADD YOUR OWN DEFINITIONS HERE ------------------------------------------
% BE SURE TO PREFACE LABEL WITH YOUR OWN INITIALS (NVR in this example) --
\newcommand{\NVRvect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\NVRtensor}[1]{\underline{\NVRvect{#1}}}
\newcommand{\NVRnorm}[1]{\left|\left|#1\right|\right|}
\newcommand{\NVRgrad}{\nabla}
\newcommand{\NVRdiv}{\NVRgrad \cdot}
\newcommand{\NVRpd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\NVRpdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
\newcommand{\NVReqdef}{\stackrel{\text{\tiny def}}{=}}

@@

% This controls the table-of-contents entry in the proceedings. Edit it
% to include your article title followed by the authors' names, as shown.
\addcontentsline{toc}{chapter}{Application of a Discontinuous Petrov-Galerkin Method to the Stokes Equations\\
{\em N.V.\ Roberts, D.\ Ridzal, P.B.\ Bochev, L.D.\ Demkowicz}}

@@

% This gives the running head. Usually you list a shortened version of
% your article title (unless it's already very short) along with
% the author's names, as shown.
\markboth{DPG Trilinos Toolbox}{N.~V.\ Roberts, D.\ Ridzal, P.~B.\ Bochev, L.~D.\ Demkowicz}

% Put your article title in here
\title{A Toolbox for a Class of Discontinuous
       Petrov-Galerkin Methods Using Trilinos\thanks{Also available as Sandia Report SAND2011-6678.
                 Sandia National Laboratories is a multi-program laboratory
                 managed and operated by Sandia Corporation, a wholly owned subsidiary of
                 Lockheed Martin Corporation, for the U.S. Department of
                 Energy's National Nuclear Security Administration under
                 contract DE-AC04-94AL85000.}}

% List each author, their affiliation, and their e-mail address, as shown.
\author{
Nathan V.\ Roberts\thanks{The University of Texas at Austin,
Institute for Computational Engineering and Science,
201 E 24th St,
Austin, TX 78712. E-mail: nroberts@ices.utexas.edu.  Research sponsored by The Center for Predictive Engineering and COmputational Sciences (PECOS). PECOS is a DOE-funded Center of Excellence within the Institute for Computational Engineering and Sciences (ICES) at The University of Texas at Austin.}
\and
Denis Ridzal\thanks{Optimization and Uncertainty Quantification, MS-1320,
                 Sandia National Laboratories, P.O. Box 5800,
                 Albuquerque, NM 87185-1320.  E-mail: dridzal@sandia.gov.
                 Research sponsored by the Office of Science ASCR program.}
\and
Pavel B.\ Bochev\thanks{Numerical Analysis and Applications, MS-1320,
                 Sandia National Laboratories, P.O. Box 5800,
                 Albuquerque, NM 87185-1320.  E-mail: pbboche@sandia.gov.
                 Research sponsored by the Office of Science ASCR program.}
\and
Leszek D.\ Demkowicz\thanks{The University of Texas at Austin,
Institute for Computational Engineering and Science,
201 E 24th St,
Austin, TX 78712. E-mail: leszek@ices.utexas.edu.. Research sponsored by PECOS.}  }

@@

% Include your abstract here.
\begin{abstract}
The class of discontinuous Petrov-Galerkin finite element methods (DPG) proposed by L. Demkowicz and J. Gopalakrishnan \cite{DPG1,DPG2} guarantees the optimality of the solution in an energy norm and produces a symmetric positive definite stiffness matrix, among other desirable properties.  In this paper, we describe a toolbox, implemented atop Sandia's Trilinos Project \cite{Trilinos}, for rapid development of solvers for DPG methods.  We use this toolbox to develop solvers for the Poisson and Stokes problems.
\end{abstract}

>>>>

% DEFINITIONS ------------------------------------------------------------
% ADD YOUR OWN DEFINITIONS HERE ------------------------------------------
% BE SURE TO PREFACE LABEL WITH YOUR OWN INITIALS (NVR in this example) --
\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\NVRtensor}[1]{\underline{\vect{#1}}}
\newcommand{\norm}[1]{\left|\left|#1\right|\right|}
\newcommand{\NVRgrad}{\nabla}
\newcommand{\NVRdiv}{\NVRgrad \cdot}
\newcommand{\NVRpd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\NVRpdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
\newcommand{\NVReqdef}{\stackrel{\text{\tiny def}}{=}}

@@

% This controls the table-of-contents entry in the proceedings. Edit it
% to include your article title followed by the authors' names, as shown.
\addcontentsline{toc}{chapter}{Application of a Discontinuous Petrov-Galerkin Method to the Stokes Equations\\
{\em N.V.\ Roberts}}

@@

% This gives the running head. Usually you list a shortened version of
% your article title (unless it's already very short) along with
% the author's names, as shown.
\markboth{Nathan Roberts Thesis Proposal}{N.~V.\ Roberts}

% Put your article title in here
\title{Applying Discontinuous Petrov-Galerkin Methods to Fluid Problems}

% List each author, their affiliation, and their e-mail address, as shown.
\author{
Nathan V.\ Roberts\thanks{The University of Texas at Austin,
Institute for Computational Engineering and Science,
201 E 24th St,
Austin, TX 78712. E-mail: nroberts@ices.utexas.edu.  Research sponsored by The Center for Predictive Engineering and COmputational Sciences (PECOS). PECOS is a DOE-funded Center of Excellence within the Institute for Computational Engineering and Sciences (ICES) at The University of Texas at Austin.} }

@@

% Include your abstract here.
\begin{abstract}
%The class of discontinuous Petrov-Galerkin finite element methods (DPG) proposed by L. Demkowicz and J. Gopalakrishnan \cite{DPG1,DPG2} guarantees the optimality of the solution in an energy norm and produces a symmetric positive definite stiffness matrix, among other desirable properties.  In this paper, we describe Camellia, a toolbox for rapid development of solvers for DPG methods, implemented atop Sandia's Trilinos Project \cite{Trilinos}, and its application to several problems in fluid dynamics.
\end{abstract}
